Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-03-03 VegOzone.tex
Include combined figure and revise its caption and referencing.

\subsubsection{Temperature, precipitation, and global irradiance}
\label{subsubsec:anomal_tpq}
In Fig.~\ref{fig:plot_temperature_anomalies_svanvik}, temperature anomalies at Svanvik are shown as percentage of days warmer/colder than $\pm 1\,\sigma$ from the climatological mean for each month. Negative deviations from climatology are displayed as negative percentage. The full annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). The summer of 2018 was significantly warmer than average. Especially in May and July more than $40\,\unit{\%}$ of days were significantly warmer than normal temperature. Temperatures continued to be significantly warmer throughout fall into early winter (August--November) with the exception of October. March 2018 was unusually cold. The summer of 2019 was fairly average, however significantly colder in July, while August was both significantly colder and warmer. Temperatures in April were significantly warmer than average.

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{temperature_signific_1}
  \includegraphics[width=8.3cm]{fig08}
  \caption{Temperature anomalies at Svanvik. Percentage of days warmer/colder than $\pm 1\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). The summer of 2018 was significantly warmer than average, especially May and July. The summer of 2019 was fairly average but significantly warmer than average in April and colder in July/August.}
  \label{fig:plot_temperature_anomalies_svanvik}
\end{figure}

In a similar way, the precipitation anomalies at Svanvik are displayed in Fig.~\ref{fig:plot_precipitation_anomalies_svanvik}. However, the percentage of days wetter/drier than $\pm \frac{1}{2}\,\sigma$ from the climatological mean is shown for each month, due to the larger variability in observed precipitation too few days showed a significance of $1 \sigma$ or higher. As above, negative deviations from the climatology are shown as negative percentage and annual positive/negative deviations are indicated in the respective corners. The hatched area between the dashed lines indicates the expected percentage of values falling above $\pm\frac{1}{2}\,\sigma$ if a normal distribution is assumed ($30.8\,\unit{\%}$). Unlike for the temperature anomalies, the picture is not as clear. While March 2018 was unusually wet, summer and fall (May/July, September/October) were significantly drier than average. 2019 was rather average throughout the year, with drier than usual fall (September/October) and a wet December.

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{precipitation_signific_1}
  \includegraphics[width=8.3cm]{fig09}
  \caption{Precipitation anomalies at Svanvik. Percentage of days wetter/drier than $\pm \frac{1}{2}\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above $\pm\frac{1}{2}\,\sigma$ if a normal distribution is assumed ($30.8\,\unit{\%}$). Summer was significantly dry only in 2018, while fall was significantly dry in both years.}
  \label{fig:plot_precipitation_anomalies_svanvik}
\end{figure}

Similarly, the global irradiance anomalies at Svanvik are presented in Fig.~\ref{fig:global_rad_signific}. The percentage of days above/below $\pm 1\,\sigma$ from the climatological mean is displayed for each month. The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed. In summer 2018 (May/July), global irradiance was significantly higher than on average, while 2019 was generally an average year with a slightly darker spring (April/May).

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{global_rad_signific_1}
  \includegraphics[width=8.3cm]{fig10}
  \caption{Global irradiance anomalies at Svanvik. Percentage of days above/below $\pm 1\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). In summer 2018 (May/July), global irradiance was significantly higher than on average, while 2019 had significantly less than normal irradiance in April/May and more in June.}
  \label{fig:global_rad_signific}
\end{figure}

@@

In accordance to the above findings, we adjust the derived ozone climatology for Svanvik by adding a constant bias correction factor $\Delta\chem{[O_3]_\mathrm{bias-corr}} = 1.2\,\unit{ppb}$ and estimate the ozone concentration anomalies for 2018/19. In Fig.~\ref{fig:ozone_signific}, the resulting percentage of days above/below $\pm 1\,\sigma$ from the bias-corrected climatological mean is displayed for each month. Negative deviations from climatology are shown as negative percentage. Note that missing bars for certain months are both due to data availability (see Section~\ref{subsubsec:atmo_svanvik} for details about the time range of data taking at Svanhovd) and anomalies not meeting the criteria of $\pm 1\sigma$ deviation from climatological mean. In April/May 2018, ozone was significantly enhanced, while 2019 was generally an average year. In both years, ozone concentrations were significantly below average in November. July 2018 has not been corrected for the missing data due to data acquisition problems. The corrected value is, however, indicated by the star (refer to Section~\ref{subsec:ozone_reco} for details of the used method for gap filling).

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{ozone_signific_1}
  \includegraphics[width=8.3cm]{fig11}
  \caption{Ozone concentration anomalies at Svanvik. Ozone climatology has been corrected for an constant negative bias of $-1.2\,\unit{ppb}$. Percentage of days above/below $\pm 1\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). July 2018 has not been corrected for the missing data due to data acquisition problems. The corrected value is indicated by the star (refer to Section~\ref{subsec:ozone_reco} for details). In April/May 2018, ozone was significantly higher than on average, while 2019 was generally an average year. In both years ozone concentrations were significantly below average in November.}
  \label{fig:ozone_signific}
\end{figure}

>>>>

\subsubsection{Temperature, precipitation, and global irradiance}
\label{subsubsec:anomal_tpq}
In Fig.~\ref{fig:anomalies_svanvik}a), temperature anomalies at Svanvik are shown as percentage of days warmer/colder than $\pm 1\,\sigma$ from the climatological mean for each month. Negative deviations from climatology are displayed as negative percentage. The full annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). The summer of 2018 was significantly warmer than average. Especially in May and July more than $40\,\unit{\%}$ of days were significantly warmer than normal temperature. Temperatures continued to be significantly warmer throughout fall into early winter (August--November) with the exception of October. March 2018 was unusually cold. The summer of 2019 was fairly average, however significantly colder in July, while August was both significantly colder and warmer. Temperatures in April were significantly warmer than average.

\begin{figure}[t]
  \includegraphics[width=12cm]{fig08-11}
  \caption{2018/19 anomalies of key environmental variables at Svanhovd displayed as percentages of days deviating from climatological mean by means of standart deviation for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates statistical significance under the assumption of a normal distribution ($15.9\,\unit{\%}$, $30.8\,\unit{\%}$ for precip.). (a) Temperature, days warmer/colder than $\pm 1\,\sigma$; (b) precipitation, days wetter/drier than $\pm \frac{1}{2}\,\sigma$; (c) global irradiance, days lighter/darker than $\pm 1\,\sigma$; (d) ozone, days higher/lower than $\pm 1\,\sigma$. The July 2018 ozone data corrected for data acquisition problems is indicated with the star (refer Section~\ref{subsec:ozone_reco} for details). The growing season of 2018 was significantly warmer, brighter, and slightly drier than average, especially in May and July. Ozone was significantly elevated in May. The growing season of 2019 was fairly average but significantly warmer than average in April and colder in July/August. No significant elevation in ozone was found.}
  \label{fig:anomalies_svanvik}
\end{figure}

%\begin{figure}[t]
  %\includegraphics[width=8.3cm]{temperature_signific_1}
  %\includegraphics[width=8.3cm]{fig08}
  %\caption{Temperature anomalies at Svanvik. Percentage of days warmer/colder than $\pm 1\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). The summer of 2018 was significantly warmer than average, especially May and July. The summer of 2019 was fairly average but significantly warmer than average in April and colder in July/August.}
  %\label{fig:plot_temperature_anomalies_svanvik}
%\end{figure}

In a similar way, the precipitation anomalies at Svanvik are displayed in Fig.~\ref{fig:anomalies_svanvik}b). However, the percentage of days wetter/drier than $\pm \frac{1}{2}\,\sigma$ from the climatological mean is shown for each month, due to the larger variability in observed precipitation too few days showed a significance of $1 \sigma$ or higher. As above, negative deviations from the climatology are shown as negative percentage and annual positive/negative deviations are indicated in the respective corners. The hatched area between the dashed lines indicates the expected percentage of values falling above $\pm\frac{1}{2}\,\sigma$ if a normal distribution is assumed ($30.8\,\unit{\%}$). Unlike for the temperature anomalies, the picture is not as clear. While March 2018 was unusually wet, summer and fall (May/July, September/October) were significantly drier than average. 2019 was rather average throughout the year, with drier than usual fall (September/October) and a wet December.

%\begin{figure}[t]
  %\includegraphics[width=8.3cm]{precipitation_signific_1}
  %\includegraphics[width=8.3cm]{fig09}
  %\caption{Precipitation anomalies at Svanvik. Percentage of days wetter/drier than $\pm \frac{1}{2}\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above $\pm\frac{1}{2}\,\sigma$ if a normal distribution is assumed ($30.8\,\unit{\%}$). Summer was significantly dry only in 2018, while fall was significantly dry in both years.}
  %\label{fig:plot_precipitation_anomalies_svanvik}
%\end{figure}

Similarly, the global irradiance anomalies at Svanvik are presented in Fig.~\ref{fig:anomalies_svanvik}c). The percentage of days above/below $\pm 1\,\sigma$ from the climatological mean is displayed for each month. The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed. In summer 2018 (May/July), global irradiance was significantly higher than on average, while 2019 was generally an average year with a slightly darker spring (April/May).

%\begin{figure}[t]
  %\includegraphics[width=8.3cm]{global_rad_signific_1}
  %\includegraphics[width=8.3cm]{fig10}
  %\caption{Global irradiance anomalies at Svanvik. Percentage of days above/below $\pm 1\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). In summer 2018 (May/July), global irradiance was significantly higher than on average, while 2019 had significantly less than normal irradiance in April/May and more in June.}
  %\label{fig:global_rad_signific}
%\end{figure}

@@

In accordance to the above findings, we adjust the derived ozone climatology for Svanvik by adding a constant bias correction factor $\Delta\chem{[O_3]_\mathrm{bias-corr}} = 1.2\,\unit{ppb}$ and estimate the ozone concentration anomalies for 2018/19. In Fig.~\ref{fig:anomalies_svanvik}d), the resulting percentage of days above/below $\pm 1\,\sigma$ from the bias-corrected climatological mean is displayed for each month. Negative deviations from climatology are shown as negative percentage. Note that missing bars for certain months are both due to data availability (see Section~\ref{subsubsec:atmo_svanvik} for details about the time range of data taking at Svanhovd) and anomalies not meeting the criteria of $\pm 1\sigma$ deviation from climatological mean. In April/May 2018, ozone was significantly enhanced, while 2019 was generally an average year. In both years, ozone concentrations were significantly below average in November. July 2018 has not been corrected for the missing data due to data acquisition problems. The corrected value is, however, indicated by the star (refer to Section~\ref{subsec:ozone_reco} for details of the used method for gap filling).

%\begin{figure}[t]
  %\includegraphics[width=8.3cm]{ozone_signific_1}
  %\includegraphics[width=8.3cm]{fig11}
  %\caption{Ozone concentration anomalies at Svanvik. Ozone climatology has been corrected for an constant negative bias of $-1.2\,\unit{ppb}$. Percentage of days above/below $\pm 1\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). July 2018 has not been corrected for the missing data due to data acquisition problems. The corrected value is indicated by the star (refer to Section~\ref{subsec:ozone_reco} for details). In April/May 2018, ozone was significantly higher than on average, while 2019 was generally an average year. In both years ozone concentrations were significantly below average in November.}
  %\label{fig:ozone_signific}
%\end{figure}
